---
title: "Did Low-Carbon Electricity Shield Countries from the Energy Price Shock?"
description: |
  Countries with higher shares of low-carbon electricity experienced smaller
  price increases after the 2022 energy crisis. We quantify the relationship
  using publicly available data.
author:
  - name: Ralf Martin
    url: https://mondpanther.github.io/wwwmondpanther/
date: 2026-03-27
output:
  distill::distill_article:
    self_contained: false
categories:
  - Climate Change
  - Energy
  - Electricity Prices
# preview: 'scatter_preview.png'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 8, fig.height = 5
)
options(repos = c(CRAN = "https://cloud.r-project.org"))
```

```{r packages, include=FALSE}
pkgs <- c("dplyr", "tidyr", "readr", "lubridate", "ggplot2", "scales",
          "stringr", "glue", "ggrepel", "plotly", "purrr", "crosstalk", "broom")
for (p in pkgs) {
  if (!requireNamespace(p, quietly = TRUE)) install.packages(p)
  suppressPackageStartupMessages(library(p, character.only = TRUE))
}
theme_set(
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(face = "bold", size = 15),
    plot.subtitle = element_text(color = "grey40", size = 11),
    panel.grid.minor = element_blank()
  )
)
```

When Russia's invasion of Ukraine sent European natural gas prices soaring in
2022, wholesale electricity prices followed. But the shock did not hit every
country equally. Countries that had invested heavily in low-carbon generation ---
nuclear, hydro, wind, solar, geothermal, and bioenergy --- saw smaller and
shorter-lived price increases than those still reliant on fossil fuels.

This analysis uses publicly available data to quantify the relationship between
a country's **pre-crisis low-carbon electricity share** and the **size of its
price increase**.

```{r download-data, include=FALSE}
# --- Wholesale prices (Ember) ---
ember_url <- paste0(
  "https://files.ember-energy.org/public-downloads/price/outputs/",
  "european_wholesale_electricity_price_data_monthly.csv"
)
prices_raw <- read_csv(ember_url, show_col_types = FALSE)
nm <- names(prices_raw)
names(prices_raw) <- c("country", "iso3", "date", "price_eur_mwh")[seq_along(nm)]

prices <- prices_raw |>
  mutate(
    date = as.Date(date),
    country = iconv(country, from = "UTF-8", to = "ASCII//TRANSLIT", sub = ""),
    price = price_eur_mwh / 10
  ) |>
  filter(!is.na(price))

# --- Generation mix (OWID) ---
owid_url <- "https://owid-public.owid.io/data/energy/owid-energy-data.csv"
energy_raw <- read_csv(owid_url, show_col_types = FALSE)

european_isos <- c(
  "ALB", "AND", "AUT", "BEL", "BGR", "BIH", "BLR", "CHE", "CYP", "CZE",
  "DEU", "DNK", "ESP", "EST", "FIN", "FRA", "GBR", "GEO", "GRC", "HRV",
  "HUN", "IRL", "ISL", "ITA", "KOS", "LTU", "LUX", "LVA", "MDA", "MKD",
  "MLT", "MNE", "NLD", "NOR", "POL", "PRT", "ROU", "SRB", "SVK", "SVN",
  "SWE", "TUR", "UKR"
)

gen_2019 <- energy_raw |>
  filter(!is.na(iso_code), iso_code != "", !str_detect(iso_code, "^OWID_"),
         iso_code %in% european_isos, year == 2019) |>
  mutate(country = iconv(country, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")) |>
  select(country, iso_code,
         gas = gas_share_elec, coal = coal_share_elec,
         nuclear = nuclear_share_elec, oil = oil_share_elec,
         hydro = hydro_share_elec, wind = wind_share_elec,
         solar = solar_share_elec, biofuel = biofuel_share_elec,
         geothermal = other_renewables_share_elec_exc_biofuel) |>
  rowwise() |>
  mutate(renewx = sum(c_across(c(solar, wind, hydro, geothermal, biofuel, nuclear)),
                      na.rm = TRUE)) |>
  ungroup()

gen_2010 <- energy_raw |>
  filter(!is.na(iso_code), iso_code != "", !str_detect(iso_code, "^OWID_"),
         iso_code %in% european_isos, year == 2010) |>
  mutate(country = iconv(country, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")) |>
  select(country, solar = solar_share_elec, wind = wind_share_elec,
         hydro = hydro_share_elec,
         geothermal = other_renewables_share_elec_exc_biofuel,
         biofuel = biofuel_share_elec, nuclear = nuclear_share_elec) |>
  rowwise() |>
  mutate(renewx_2010 = sum(c_across(c(solar, wind, hydro, geothermal, biofuel, nuclear)),
                           na.rm = TRUE)) |>
  ungroup() |>
  select(country, renewx_2010)

annual_avg <- prices |>
  mutate(year = year(date)) |>
  group_by(country, year) |>
  summarise(avg_price = mean(price, na.rm = TRUE), .groups = "drop")

price_2019 <- annual_avg |> filter(year == 2019) |>
  select(country, price_2019 = avg_price)

avg_post <- annual_avg |>
  filter(year >= 2023, year <= 2025) |>
  group_by(country) |>
  summarise(price_post = mean(avg_price, na.rm = TRUE), .groups = "drop")

change <- price_2019 |>
  inner_join(avg_post, by = "country") |>
  filter(price_2019 > 0) |>
  mutate(price_change = price_post - price_2019) |>
  arrange(price_change)

reg_data <- change |>
  inner_join(gen_2019 |> select(country, renewx), by = "country") |>
  filter(!is.na(renewx))
```

## The price shock across Europe

The chart below shows monthly wholesale electricity prices for every European
country in the Ember dataset. Looking at wholesale prices is useful to understand the true impact on generation costs. Many countries imposed price ceilings or provided subsidies to end users which distort retail prices. Use the dropdown to select specific countries, or
view them all at once.

```{r time-series-filter}
sd_prices <- SharedData$new(prices, key = ~country, group = "ts_group")

filter_select(
  id = "country_filter",
  label = "Select countries to highlight",
  sharedData = sd_prices,
  group = ~country,
  multiple = TRUE
)
```

```{r time-series-plot}
plot_ly(sd_prices, x = ~date, y = ~price, color = ~country,
        type = "scatter", mode = "lines", line = list(width = 1.3),
        hovertemplate = "%{x|%b %Y}<br>%{y:.2f} c/kWh<extra>%{fullData.name}</extra>") |>
  layout(
    xaxis = list(title = ""),
    yaxis = list(title = "Wholesale price (cents / kWh)"),
    height = 400,
    legend = list(orientation = "v", x = 1.02, y = 1, font = list(size = 8)),
    hovermode = "x unified",
    margin = list(t = 10)
  ) |>
  highlight(on = "plotly_click", off = "plotly_doubleclick",
            persistent = TRUE, selectize = FALSE)
```

<aside>Source: Ember European Wholesale Electricity Price Data (monthly).</aside>

## Who got hit hardest?

To measure the lasting impact --- rather than just the 2022 spike --- we compare
each country's **2019 average price** with its **average over 2023--2025**.

```{r bar-chart}
d_bar <- change |>
  mutate(
    country = factor(country, levels = country),
    col = ifelse(price_change > 0, "#e74c3c", "#2980b9")
  )

plot_ly(d_bar, y = ~country, x = ~price_change,
        type = "bar", orientation = "h",
        marker = list(color = ~col),
        text = ~paste0(ifelse(price_change > 0, "+", ""),
                       round(price_change, 2), " c/kWh"),
        textposition = "outside", textfont = list(size = 10),
        hovertemplate = paste0(
          "<b>%{y}</b><br>",
          "Change: %{x:.2f} c/kWh<br>",
          "2019: %{customdata[0]:.2f} c/kWh<br>",
          "Avg 2023-25: %{customdata[1]:.2f} c/kWh<extra></extra>"
        ),
        customdata = ~cbind(price_2019, price_post)) |>
  layout(
    xaxis = list(title = "Price change (cents / kWh)"),
    yaxis = list(title = "", categoryorder = "trace"),
    height = max(380, nrow(d_bar) * 18),
    margin = list(l = 120, r = 60),
    showlegend = FALSE
  )
```

<aside>Difference between the average wholesale price in 2023--2025 and the
2019 baseline. Red = increase; blue = decrease.</aside>

## The low-carbon advantage

Is there a systematic relationship between a country's pre-crisis electricity
mix and the size of its price shock? We measure each country's **low-carbon
share** in 2019 --- the combined share of nuclear, hydro, wind, solar,
geothermal, and bioenergy --- and plot it against the price change.

```{r scatter-plot, fig.width=9, fig.height=6.5}
fit <- lm(price_change ~ renewx, data = reg_data)
s   <- summary(fit)
r2  <- round(s$r.squared, 3)
slope <- round(coef(fit)[2], 4)
se_slope <- round(s$coefficients[2, 2], 4)

slope_sign <- ifelse(slope < 0, "", "+")
slope_label <- glue("Slope: {slope_sign}{slope} c/kWh per pp  (SE = {se_slope})")

ggplot(reg_data, aes(renewx, price_change)) +
  geom_smooth(method = "lm", se = TRUE, colour = "#e67e22", fill = "#e67e22",
              alpha = 0.15, linewidth = 1.2) +
  geom_point(colour = "#2980b9", size = 3, alpha = 0.85,
             shape = 21, fill = "#2980b9", stroke = 0.5) +
  ggrepel::geom_text_repel(
    aes(label = country),
    size = 3.2, colour = "#2c3e50",
    max.overlaps = Inf,
    box.padding = 0.4,
    point.padding = 0.3,
    segment.color = "grey70",
    segment.size = 0.3,
    min.segment.length = 0.2,
    seed = 42
  ) +
  annotate("text",
    x = max(reg_data$renewx) * 0.97,
    y = max(reg_data$price_change) * 0.95,
    label = slope_label,
    hjust = 1, size = 4, colour = "#e67e22", fontface = "bold"
  ) +
  annotate("text",
    x = max(reg_data$renewx) * 0.97,
    y = max(reg_data$price_change) * 0.85,
    label = glue("R\u00b2 = {r2}"),
    hjust = 1, size = 3.8, colour = "#e67e22"
  ) +
  labs(
    x = "Low-carbon electricity share in 2019 (%)",
    y = "Price change: 2019 vs avg 2023\u20132025 (cents / kWh)"
  )
```

&copy; Ralf Martin

> For every additional percentage point of low-carbon electricity in 2019, the
> post-crisis price increase was **`r round(coef(fit)[2], 3)` cents/kWh
> smaller** on average.

## Regression results

```{r regression-table}
broom::tidy(fit, conf.int = TRUE) |>
  mutate(across(where(is.numeric), ~round(.x, 4))) |>
  knitr::kable(
    col.names = c("Term", "Estimate", "Std. Error", "t", "p-value",
                  "CI low (2.5%)", "CI high (97.5%)"),
    caption = glue("OLS: price change ~ low-carbon share. N = {nrow(reg_data)}, R\u00b2 = {r2}, Adj. R\u00b2 = {round(s$adj.r.squared, 3)}")
  )
```

## What if countries hadn't expanded low-carbon power?

Between 2010 and 2019 many European countries significantly increased their
low-carbon electricity share. Using the regression slope, we ask: **how much
higher would the post-crisis price increase have been if each country had stayed
at its 2010 low-carbon share?**

```{r counterfactual}
slope_est <- coef(fit)[2]

cf <- reg_data |>
  inner_join(gen_2010, by = "country") |>
  filter(!is.na(renewx_2010)) |>
  mutate(
    renewx_gain    = renewx - renewx_2010,
    price_saving   = renewx_gain * slope_est,
    counterfactual = price_change - price_saving
  ) |>
  arrange(desc(renewx_gain))
```

```{r counterfactual-scatter, fig.width=9, fig.height=6.5}
ggplot(cf, aes(renewx_gain, price_saving)) +
  geom_point(colour = "#27ae60", size = 3, alpha = 0.85,
             shape = 21, fill = "#27ae60", stroke = 0.5) +
  ggrepel::geom_text_repel(
    aes(label = country),
    size = 3.2, colour = "#2c3e50",
    max.overlaps = Inf,
    box.padding = 0.4,
    point.padding = 0.3,
    segment.color = "grey70",
    segment.size = 0.3,
    min.segment.length = 0.2,
    seed = 42
  ) +
  labs(
    x = "Increase in low-carbon share, 2010 to 2019 (pp)",
    y = "Implied price saving (cents / kWh)"
  )
```

<aside>The x-axis shows how much the low-carbon share grew between 2010 and
2019; the y-axis shows the implied reduction in the post-crisis price
increase.</aside>

```{r counterfactual-bar}
cf_long <- cf |>
  select(country, Actual = price_change, Counterfactual = counterfactual) |>
  arrange(Actual) |>
  mutate(country = factor(country, levels = country)) |>
  pivot_longer(cols = c(Actual, Counterfactual),
               names_to = "scenario", values_to = "change")

plot_ly(cf_long, y = ~country, x = ~change, color = ~scenario,
        type = "bar", orientation = "h",
        colors = c("Actual" = "#2980b9", "Counterfactual" = "#e74c3c"),
        hovertemplate = paste0("<b>%{y}</b><br>",
                               "%{fullData.name}: %{x:.2f} c/kWh<extra></extra>")) |>
  layout(
    barmode = "group",
    xaxis = list(title = "Price change (cents / kWh)"),
    yaxis = list(title = "", categoryorder = "trace"),
    height = max(380, n_distinct(cf$country) * 20),
    margin = list(l = 120),
    legend = list(x = 0.7, y = 0.05, bgcolor = "rgba(255,255,255,0.8)")
  )
```

<aside>Blue = actual price change. Red = counterfactual if the country had
stayed at its 2010 low-carbon share.</aside>

## Total annual savings from low-carbon expansion

How much money did countries save by expanding their low-carbon electricity
share between 2010 and 2019? We take the implied per-kWh price saving from
the regression (slope &times; gain in low-carbon share) and multiply it by actual
electricity demand in each of 2023, 2024, and 2025.

```{r cost-saving}
# Get electricity demand for 2023-2025 (in TWh)
demand_post <- energy_raw |>
  filter(!is.na(iso_code), iso_code != "", !str_detect(iso_code, "^OWID_"),
         iso_code %in% european_isos, year %in% 2023:2025) |>
  mutate(country = iconv(country, from = "UTF-8", to = "ASCII//TRANSLIT", sub = "")) |>
  select(country, iso_code, year, demand_twh = electricity_demand) |>
  filter(!is.na(demand_twh))

saving_yearly <- cf |>
  select(country, price_saving) |>
  cross_join(tibble(year = 2023:2025)) |>
  left_join(demand_post, by = c("country", "year")) |>
  filter(!is.na(demand_twh)) |>
  mutate(saving_bn = price_saving * demand_twh / 100)

saving_df <- saving_yearly |>
  group_by(country) |>
  summarise(
    avg_saving_bn = mean(saving_bn, na.rm = TRUE),
    n_years = n(),
    .groups = "drop"
  ) |>
  arrange(avg_saving_bn) |>
  mutate(country = factor(country, levels = country))

total_saving <- round(sum(saving_df$avg_saving_bn, na.rm = TRUE), 1)

saving_df <- saving_df |>
  mutate(col = ifelse(avg_saving_bn < 0, "#27ae60", "#e74c3c"))

plot_ly(saving_df, y = ~country, x = ~avg_saving_bn,
        type = "bar", orientation = "h",
        marker = list(color = ~col),
        text = ~paste0(round(avg_saving_bn, 2), " bn EUR"),
        textposition = "outside", textfont = list(size = 11),
        hovertemplate = paste0(
          "<b>%{y}</b><br>",
          "Annual saving: %{x:.2f} bn EUR<extra></extra>"
        )) |>
  layout(
    xaxis = list(title = "Annual saving from low-carbon expansion (billion EUR)"),
    yaxis = list(title = "", categoryorder = "trace"),
    height = max(380, n_distinct(saving_df$country) * 20),
    margin = list(l = 120, r = 80, b = 100),
    showlegend = FALSE,
    annotations = list(
      list(
        text = paste0(
          "Implied saving = regression slope \u00d7 low-carbon gain (2010\u20132019) ",
          "\u00d7 actual demand (avg 2023\u20132025).<br>",
          "Green = saved; red = lost. ",
          "Total: \u20ac", abs(total_saving), "bn/year saved."
        ),
        xref = "paper", yref = "paper",
        x = 0, y = -0.15, showarrow = FALSE,
        font = list(size = 10, color = "#7f8c8d"),
        xanchor = "left"
      )
    )
  )
```

<aside>Each bar shows the estimated annual saving from expanding low-carbon
generation between 2010 and 2019, multiplied by actual demand in 2023--2025.</aside>

## Data & methodology

| Item | Detail |
|------|--------|
| **Prices** | Ember European Wholesale Electricity Price Data (monthly) |
| **Generation mix** | Our World in Data / Ember + Energy Institute |
| **Price unit** | Euro-cents per kWh |
| **Base year** | 2019 (pre-pandemic, pre-crisis) |
| **Comparison** | Average of 2023--2025 |
| **Low-carbon share** | Nuclear + hydro + wind + solar + geothermal + bioenergy |
| **Method** | OLS regression of price change on 2019 low-carbon share |
