---
title: "Welcome to my space in cyberspace"
description: 
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

I am an Associate Professor of Economics @ Imperial College Business School
[Imperial College Business School](https://www.imperial.ac.uk/people/r.martin), London (Europe). I also direct the Growth Programme at the [Centre for Economic Performance](http://cep.lse.ac.uk/_new/staff/person.asp?id=739) @ the London School of Economics.

In my research I am trying to focus on things that help to increase economic productivity without compromising the natural environment. I am also concerned about the effects and causes of online mis-information and the re-emergence of bigotism. Some of my other passions include cycling (particularly in London) and windsurfing.

[Google Scholar Profile](https://scholar.google.com/citations?user=ssPVmxMAAAAJ&hl=en)  |  [On Twitter](https://twitter.com/mondpanther)

```{r , include=FALSE, eval=FALSE, echo=FALSE}
#<!--html_preserve-->

#<a href="https://twitter.com/mondpanther?ref_src=twsrc%5Etfw" class="twitter-follow-button" data-show-count="false">Follow @mondpanther</a><script async #src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>

#<!--/html_preserve-->

```
