---
title: "Research"
description: |
output:
  distill::distill_article:
    self_contained: false
    css: webex.css    
    includes:
      after_body: webex.js

    toc: true
    toc_depth: 2
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#library("webex")
```

```{r,evel=FALSE,message=FALSE}
#this seems promising:  
  
#  https://github.com/ijlyttle/codefolder

#install.packages("devtools")
#devtools::install_github("ijlyttle/codefolder")

#library(codefolder)

```



# Publications


## Academic Articles

### [Do Tax Incentives Increase Firm Innovation? An RD Design for R&D, Patents, and Spillovers](https://www.aeaweb.org/articles?id=10.1257/pol.20200739&from=f)
Antoine Dechezleprêtre, Elias Einiö, Ralf Martin, Kieu-Trang Nguyen, John Van Reenen, AMERICAN ECONOMIC JOURNAL: ECONOMIC POLICY (FORTHCOMING)

### [Environmental Preferences and Technological Choices: Is Market Competition Clean or Dirty?](https://www.aeaweb.org/articles?id=10.1257/aeri.20210014)
Philippe Aghion,,Roland Bénabou,,Ralf Martin,Alexandra Roulet,AMERICAN ECONOMIC REVIEW: INSIGHTS,VOL. 5, NO. 1, MARCH 2023

### [Searching for carbon leaks in multinational companies.](https://www.sciencedirect.com/science/article/pii/S0095069621001406)
Antoine Dechezleprêtre, Caterina Gennaioli, Ralf Martin, and Mirabelle Muûls (2022).  Journal of Environmental Economics and Management
Volume 112, March 2022
      

### [Some Causal Effects of an Industrial Policy](https://www.aeaweb.org/articles?id=10.1257/aer.20160034)
Criscuolo, Chiara, Ralf Martin, Henry G. Overman, and John Van Reenen. (2019). American Economic Review, 109 (1): 48-85.


### [Carbon Taxes, Path Dependency, and Directed Technical Change: Evidence from the Auto Industry](https://www.journals.uchicago.edu/doi/abs/10.1086/684581)
Philippe Aghion & Antoine Dechezleprêtre & David Hémous & Ralf Martin & John Van Reenen, (2016). Journal of Political Economy, University of Chicago Press, vol. 124(1) 


### [The Impact of the European Union Emissions Trading Scheme on Regulated Firms: What Is the Evidence after Ten Years?](https://www.journals.uchicago.edu/doi/10.1093/reep/rev016)
Ralf Martin, Mirabelle Muûls, and Ulrich J. Wagner (2016)  Review of Environmental Economics and Policy 10 (1): 129-148 doi:10.1093/reep/rev016



### [Competition and norms: A self-defeating combination?](http://dx.doi.org/10.1016/j.enpol.2016.06.001)
Genevieve Alberts, Zeynep Gurguc, Pantelis Koutroumpis, Ralf Martin, Mirabelle Muûls, Tamaryn Napp (2016) Energy Policy, Volume 96, September 2016, Pages 504-523


### [Industry compensation under relocation risk: A firm-level analysis of the EU emissions trading scheme](http://tiny.cc/53y2yx)
Martin, R., Muuls, M., de Preux, L., & Wagner, U. (2014). American Economic Review, 104(8): 2482-2508.


### [The impacts of the climate change levy on manufacturing: Evidence from microdata](http://tiny.cc/ag02yx)
Martin, R., de Preux, L. B., & Wagner, U. J. (2014). Journal of Public Economics.  Volume 117, September 2014, Pages 1–14. URL: 

### [On the Empirical Content of Carbon Leakage Criteria in the EU Emissions Trading Scheme](http://tiny.cc/sh02yx) 
Martin, R., Muuls, M., de Preux, L., & Wagner, U. (2014). Ecological Economics Volume 105. September 2014, Pages 78-88.  


### Anatomy of a Paradox: Management Practices, Organizational Structure and Energy Efficiency
Ralf Martin, Mirabelle Muuls, Laure de Preux and Ulrich Wagner (2012), Journal of Environmental Economics and Management, Volume 63, Issue 2, March 2012, Pages 208–223

### Modern management: Good for the environment or just hot air?
Nick Bloom, Christos Genakos, Ralf Martin and Raffaella Sadun (2010), Economic Journal, Royal Economic Society, vol. 120(544), pages 551-572, 05. https://doi.org/10.1111/j.1468-0297.2010.02351.x 

### Multinationals and US Productivity Leadership
Chiara Criscuolo and Ralf Martin (2009), Review of Economics and Statistics, May 2009, 91(2): 263–281. 

### Import Competition, Productivity, and Restructuring in UK Manufacturing
Chiara Criscuolo, Jonathan Haskel and Ralf Martin (2004), Oxford Review of Economic Policy, Volume 20, Issue 3, Autumn 2004, pages 393-408. https://doi.org/10.1093/oxrep/grh023 



## Working papers

### [Does pricing carbon mitigate climate change? Firm-level evidence from the European Union emissions trading scheme](http://cep.lse.ac.uk/pubs/download/dp1728.pdf)
Jonathan Colmer, Ralf Martin, Mirabelle Muuls, Ulrich Wagner (2021). CEP Discussion Paper 1728  


### Making Smart Meters Smarter
Greer Gosnell, Ralf Martin, Mirabelle Muûls, Quentin Coutellier, Goran Strbac, Simon Tindermans (2019) CEP Discussion Paper 1602, http://cep.lse.ac.uk/pubs/download/dp1602.pdf

### Knowledge Spillovers from Clean and Dirty Technologies
Antoine Dechezleprêtre, Ralf Martin, Myra Mohnen (2014).  CEP Discussion Paper 1300. http://cep.lse.ac.uk/pubs/download/dp1300.pdf


### Productivity Spreads, Market Power Spreads and Trade
Ralf Martin (2010) CEP Discussion Paper 965, http://cep.lse.ac.uk/pubs/download/dp0965.pdf.



## Policy Papers



### Sustainable Growth in the UK: Seizing opportunities from technological change and the transition to a low-carbon economy
James Rydge, Ralf Martin and Anna Valero (2019) CEP Industrial Strategy Paper CEPIS07.


# Research Topics

## Adoption of prosocial Technology

One pathway for transition to a clean economy is the wide spread adoption of pro social technologies; i.e. technologies with positive values for others rather than the adopter. We study the adoption of such a technology by building a virtual power plant.

- [Powbal](https://powbalenergy.net/)


## Design and evaluation of Industrial Policy
Industrial policy in the form of targeted support for specific sectors or technologies enjoys a renaissance. But which sectors exactly should be supported? I argue that governments should identify existing market failures and use industrial policy to correct these if no other tools are available. The most obvious market failure relevant to this are differences in knowledge spillovers from different technologies. I develop the idea over a number of different reports and papers including:

- [Sustainable growth in the UK](http://cep.lse.ac.uk/_new/publications/abstract.asp?index=6073)
- [Some Causal Effects of an Industrial Policy](https://www.aeaweb.org/articles?id=10.1257/aer.20160034)


## Evaluation of Climate Change Policy

Does climate policy do what it says on the tin?

- [The impact of a carbon tax on manufacturing](https://www.sciencedirect.com/science/article/pii/S0047272714001078)

- [Industry Compensation under Relocation Risk: A Firm-Level Analysis of the EU Emissions Trading Scheme](https://www.aeaweb.org/articles?id=10.1257/aer.104.8.2482)

## What determines the direction of innovation?

Innovation is the key driver of economic growth. However, not all technologies generate the same externalities. Therefore it is important to know the flavour of innovation in addition to the quantity.

- [Environmental Preferences and Technological Choices: Is Market Competition Clean or Dirty?](http://cep.lse.ac.uk/_new/publications/abstract.asp?index=6964)

- [Carbon Taxes, Path Dependency, and Directed Technical Change: Evidence from the Auto Industry](https://www.journals.uchicago.edu/doi/10.1086/684581)

## The causes and consequence of online mis-information

There is no doubt much dis-information on social media. However, does this make any difference for tangible and relevant outcomes such as who wins elections or who gets infected in a pandemic?


- [Infections of the body and the mind](https://mondpanther.github.io/economemics.github.io/mindbody.html)
