---
title: "Management practices and Environmental Regulation in China"
description: |
  Better managemened firms are responding more effectively
author:
  - name: Ralf Martin
    url: https://mondpanther.github.io/wwwmondpanther/
date: "`r Sys.Date()`"
output:
  distill::distill_article:
    self_contained: true
#    css: ../../webex.css
#    includes:
#      after_body: ../../webex.js
categories:
  - Climate Change
  - Management
  - ETS
editor_options: 
  chunk_output_type: inline
---









Recent literature has emphasized the importance of management practices for firm performance, including the environmental impact of businesses.
Here we consider how variation in management quality affects the response of firms to environmental regulation, specifically the nascent Chinese Emission Trading System. We find that businesses that are better managed are more responsive to price incentives implied by carbon trading. More details [here](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3797466)



```{r setup, include=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE,warning=FALSE)

library(haven)

ets = read_dta("https://www.dropbox.com/s/r1e53jhba54xqnm/mcchinadata_forexploration_long.dta?dl=1")


library(dplyr)


```

```{r include=FALSE,message=FALSE}
library(knitr)
#read_chunk("https://www.dropbox.com/s/aic10h7p1dozdr9/prepdata.R?dl=1")
```

```{r prep data,include=FALSE,message=FALSE}

library(tidyr)
library(magrittr)
library(dplyr)
ets %<>% mutate(lnelec=log(m312),
                ln1Pelec=log(1+m312),
                lncoal=log(m313),
                ln1Pcoal=log(1+m313),
                lnoil=log(m314),
                ln1Poil=log(1+m314),
                lnwater=log(m315),
                ln1Pwater=log(1+m315),
                elec=m312,
                coal=m313,
                oil=m314,
                water=m315) %>% 
                rowwise() %>% mutate(
                zets_anticip=mean(c(zets2017, zets2_stg, zets2_tgh, zauct_allowce, zsanc_stg),na.rm=T))

test=ets %>% select(zets_anticip)



library(readr)
#write_csv(ets,"../../Apps/Overleaf/McChinaETSdata/mcchinadata_forexploration_long.csv")
# Figure out OK obs

ets %<>% group_by(uniqid) %>% arrange(uniqid,year) %>% 
         mutate(Lelec=dplyr::lag(elec),
                okid=((elec>0&!is.na(elec))|
                      (coal>0&!is.na(coal))|
                      (oil>0&!is.na(oil))>0) )  

#ets= ets %>% filter(elec>0 | (dplyr::lag(elec)==0 & elec==0) )  %>% ungroup()
table(ets$nace)
#test=ets %>% select(okid,lnelec,year,elec,coal,oil,water,uniqid,okid) %>% filter(okid==T)




etsf=ets %>% filter(okid & fp_hubei==0
                    ) %>% group_by(uniqid) %>% 
     mutate(miny=min(year),maxy=max(year)) %>% 
     filter( miny<2013 & maxy>=2013 & year<=2015 & year>=2007)

etsf[is.na(etsf)]=NA

#etsf %>% group_by(year) %>% summarize(mean(elec==0),mean(coal==0),n())
test=etsf %>% select(zenvmgt_index_Opt4,zets_anticip,zets_rational,uniqid,year)

etsf=etsf %>% mutate(preid=year<2013,postid=year>=2013)

mmean=function(x)mean(x,na.rm=T)
etsfpre=etsf %>% filter(year<2013) %>% group_by(uniqid,etsfirm) %>% 
        summarise_at(vars(elec,coal,oil,water,zenvmgt_index_Opt4,zets_anticip,zets_rational),mmean)     

grr  =function(x) ifelse(x+dplyr::lag(x)==0,0,(x-dplyr::lag(x))/(x+dplyr::lag(x))*2)
dd=function(x) (x-dplyr::lag(x))
dd1P=function(x) (log(1+x)-log(1+dplyr::lag(x)))

etsby=etsf %>%    group_by(uniqid,preid,etsfirm,nace) %>% 
        summarise_at(vars(elec,coal,oil,water,year),mmean)     %>% 
        arrange(uniqid,-preid) %>% group_by(uniqid) %>%
        mutate(grcoal=grr(coal),groil=grr(oil),grelec=grr(elec),grwater=grr(water),
               ddcoal=dd(coal),ddoil=dd(oil),ddelec=dd(elec),ddwater=dd(water),
               dd1Pcoal=dd1P(coal),dd1Poil=dd1P(oil),dd1Pelec=dd1P(elec),dd1Pwater=dd1P(water))
        


qs=function(x) {
  ddd=etsfpre %>% ungroup()
  qvar=x#[ddd$etsfirm==1]
  cut(x, breaks = c(-1,as.vector(quantile(qvar,probs=c(.5,1) ,na.rm=T))),
      labels=c("50","100"))
}

#aaa=quantile(etsfpre$oil,probs=c(.2,.6))
#as.vector(aaa)
#test=etsfpre %>% ungroup() %>%  mutate(tt=qs(oil))
#gg=test %>% filter(tt=="100")

etsfpre=etsfpre %>% ungroup() %>%  mutate(qoil=qs(oil),manage=qs(zenvmgt_index_Opt4),rational=qs(zets_rational), anticip =qs(zets_anticip),
                           qcoal=qs(coal),
                           qelec=qs(elec),
                           qwater=qs(water)) %>% 
                           select(uniqid,qcoal,qelec,qwater,qoil,manage,rational,anticip)

etsf=etsf %>% inner_join(etsfpre,by="uniqid")

```


```{r more data prep, include=FALSE,message=FALSE}

etsbyXpre=etsby %>% inner_join(etsfpre,by="uniqid")

#etsbyX#
etsf=etsf %>% mutate(inETS=(etsfirm==1 & year>=2013 & fp_hubei==0 ) | (etsfirm==1 & year>=2013 &fp_hubei==1 ))
#names(etsf)
#lm(coal~inETS+factor(year),etsf) %>% summary()

library(fixest)

df=etsf %>% select(preid , coal,inETS,uniqid,year,qcoal,qelec,qwater,qoil,oil,elec,water,manage,
                   rational,anticip,
                   ends_with("coal"),ends_with("oil") ,ends_with("elec"),
                   ends_with("water"),
                   etsfirm)
df=do.call(data.frame,lapply(df, function(x) replace(x, is.infinite(x),NA)))
#df= df %>% mutate()

#df=df %>% filter(qcoal==100)
table(df$year)

df=df %>% group_by(uniqid) %>% mutate(miny=min(year),maxy=max(year),
                                      inETSXtop=inETS*(qcoal=="100"),
                                      inETS=as.numeric(inETS))
df%<>%filter(miny<2013&maxy>=2013)

df%<>%mutate(rationl=ifelse(etsfirm==0,0,rational),rationl=ifelse(anticip==0,0,anticip))

```



```{r prepare descriptive stats,include=FALSE,message=FALSE}
obsdelta=etsbyXpre %>% filter(!is.na(grcoal)) %>%   group_by(etsfirm,manage)  %>% dplyr::summarise(nn=n())

obs=df %>% filter(!is.na(coal)) %>%  group_by(etsfirm,manage) %>% dplyr::summarise(nn=n())

firms=df %>% filter(!is.na(coal)) %>%  distinct(uniqid,.keep_all=T) %>%  
     group_by(etsfirm,manage) %>% dplyr::summarise(nn=n())

```



```{r}
set.seed(1206)

q <- data.frame(p = rep(c("A","B"),each = 10,len = 30), 
                a = rep(c(1,2,3),each = 10),
                id = seq(30),
                b = round(runif(30,10,20)),
                c = round(runif(30,40,70)))
library(tables)



tab <- tabular((Factor(etsfirm)*Factor(manage)+1) ~ (N = 1) + (coal + oil + elec + water) * (mean + sd),
               data = etsbyXpre %>% filter(preid))
ttt1=tab[ tab[,1] > 0, ]

library(kableExtra)
library(Hmisc)

dtable=function(fuel){
  #fuel="coal"
  qfuel=paste0("q",fuel)
  nn=paste("n",fuel)
  nm=paste("m",fuel)
  
  ff=etsbyXpre   %>% 
     group_by(etsfirm,!!sym(qfuel)) %>% 
     summarise( n=n(),
                m=mean(!!sym(fuel)) )  
     
     
}
res=dtable("coal") %>% rename(ncoal=n,mcoal=m)
res=bind_cols(res,dtable("oil")  %>% rename(noil=n,moil=m))
res=bind_cols(res,dtable("elec") %>% rename(nelec=n,melec=m))
res=bind_cols(res,dtable("water") %>% rename(nwater=n,mwater=m))


```



# A Grahpical Summary

```{r,include=FALSE,echo=FALSE,warning=FALSE}

library(ggplot2)
library(ggridges)
library(gridExtra)
library(grid)
library(png)
#library(downloader)
#library(grDevices)
#library(plyr)

#etsfirm=recode(factor(etsfirm),`0`="non ETS",
                                              #`1`="ETS"),etsfirm=relevel(etsfirm,ref="non ETS"),

etsbyXpre=etsbyXpre %>% mutate(etsfirm=factor(etsfirm))
test=etsbyXpre%>%mutate(      etsfirm=relevel(etsfirm,ref="0"))

etsbyXpre=test %>%   mutate(                 etsfirm=recode(etsfirm, 
                                                 `0`  = "Non ETS",
                                                 `1` = "ETS" ),
                               manage=recode(manage, 
                                                 `50`  = "Below Median",
                                                 `100` = "Above Median" ))
      
#etsbyXpre <- within(etsbyXpre, etsfirm <- relevel(etsfirm, ref = "non ETS"))
                               
grpics=function(x,label=""){
  etsbyXpre["xxx"]=etsbyXpre[x]
  
  mmn=mean(etsbyXpre$xxx)
  mms=as.character(mmn)
  
  etsbyXpre %>%   ggplot() + xlab(label)+ ylab("Management Quality") +
  scale_fill_discrete( name = "" , labels=) +
  geom_density_ridges(  aes(x = xxx, y=manage,  fill = factor(etsfirm)),alpha=.3,scale=1.1) + 
  theme_minimal()  + theme(legend.position="bottom")+ annotate("text", x=mmn, y=2, label= mms) 
    
  
}



p1=grpics("grcoal", label="Growth of Coal")
p2=grpics("groil",  label="Growth of Oil")
p3=grpics("grelec", label="Growth of Electricity")
p4=grpics("grwater",label="Growth of Water")


g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p1)
```

```{r densityplots,echo=FALSE,warning=FALSE}

grid.arrange(arrangeGrob(p1 + theme(legend.position="none"),
                         p2 + theme(legend.position="none"),
                         p3 + theme(legend.position="none"),
                         p4 + theme(legend.position="none"),
                         nrow=2),
             mylegend, nrow=2,heights=c(10, 1))


```

