---
title:  MULAMA Roulette 
subtitle: Monte Carlo Analysis of the MULAMA production function framework
output: html_document
runtime: shiny
---







```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Context

Let's assume

$$\mu_{it}=1+\alpha_{\mu,i}+\nu_{\mu,it}$$
Normalizing the economy wide variables to 1 we can write demand as
$$ Q_{it}=\Lambda_{it}^{\eta_{it}-1}P_{it}^{\eta_{it}} $$
where
$$
\mu=\frac{1}{1-\frac{1}{\eta}}=\frac{\eta}{\eta-1}
$$
and 
$$
\eta=\frac{\mu}{\mu-1}
$$
Hence

$$P=\Lambda^{\frac{\eta-1}{\eta}}Q^{-\frac{1}{\eta}}$$

Firm level profits become



$$V_{it}(K_{it})=\max_{L,M}\left\{ \Lambda_{it}^{\frac{1}{\mu}}Q_{it}^{\frac{1}{\mu_{it}}}-LW_{Lit}-MW_{Mit}\right\} $$
First order conditions require:
$$
M=\frac{\alpha_M Q^{\frac{1}{\mu}}}{\mu W_M}\Lambda^{\frac{1}{\mu}}
(\#eq:M)
$$

(for simplicity ignore firm and time subscripts)




We can plug this into the production function
$$
Q=AK^{\alpha_{K}}L^{\alpha_{L}}\left(\frac{\alpha_{M}Q^{\frac{1}{\mu}}}{\mu W_{M}}\Lambda^{\frac{1}{\mu}}\right)^{\alpha_{M}}
$$
and solve for Q:

$$
Q^{*}=\left[AK^{\alpha_{K}}L^{\alpha_{L}}\left(\frac{\alpha_{M}}{W_{M}}\right)^{\alpha_{M}}\frac{\Lambda^{\frac{\alpha_{M}}{\mu}}}{\mu^{\alpha_{M}}}\right]^{\frac{\mu}{\mu-\alpha_{M}}}
(\#eq:M)
$$


Also note that if capital and labour were flexible in the short run we would have
$$
L=\frac{\alpha_{L}Q^{\frac{1}{\mu}}}{\mu W_{L}}\Lambda^{\frac{1}{\mu}}
$$

$$
K=\frac{\alpha_K Q^{\frac{1}{\mu}}}{\mu W_K}\Lambda^{\frac{1}{\mu}}
(\#eq:K)
$$
where $W_K$ is the user cost of capital and $\alpha_K=\gamma-\alpha_L-\alpha_M$


With this we can work out optimal output $Q^{FLEX}$ - the amount of output if all factors were flexible - as

$$
Q^{FLEX}=\left[A\left(\frac{\alpha_{L}}{W_{L}}\right)^{\alpha_{L}}\left(\frac{\alpha_{M}}{W_{M}}\right)^{\alpha_{M}}\left(\frac{\alpha_{K}}{W_{K}}\right)^{\alpha_{K}}\frac{\Lambda^{\frac{\alpha_{K}+\alpha_{L}+\alpha_{M}}{\mu}}}{\mu^{\alpha_{K}+\alpha_{L}+\alpha_{M}}}\right]^{\frac{\mu}{\mu-\alpha_{L}-\alpha_{M}-\alpha_{K}}}
$$


We assume that labor and capital evolve converging to the level consistent with flexible levels but with a random deviations $\nu_{L}$ and $\nu_{K}$ so that
$$
L=LAG\left(\frac{\alpha_{L}\left(Q^{FLEX}\right)^{\frac{1}{\mu}}}{\mu W_{L}}\Lambda^{\frac{1}{\mu}}\right)\times\exp\nu_{L}
$$

$$
K=LAG\left(\frac{\alpha_{K}\left(Q^{FLEX}\right)^{\frac{1}{\mu}}}{\mu W_{K}}\Lambda^{\frac{1}{\mu}}\right)\times\exp\nu_{K}
$$



```{r, include=FALSE}


#source("mulama_roulette_croupier.R")
        firms=100
        periods=10
        
        alphL=0.3
        alphM=0.6
        gam=1.2
        
        
        signua=1/4
        signulam=1/4
        signumu=1/4
        
        sigalphmu=1
        signuk=1
        signul=1
        
        philam=.5
        phia=.4
        
        repli=30
        
       source("mulama_roulette_croupier.R")



```



# Parameter setup

```{r eruptions, echo=FALSE}
#inputPanel
fluidPage(

    sliderInput("firms",
                  "Number of firms",
                  min = 10,
                  max = 1000,
                  value = firms),
    
    sliderInput("periods",
                  "Number of periods",
                  min = 2,
                  max = 100,
                  value = periods),
    
    sliderInput("alphL",
                  "\\(\\alpha_L\\)",
                  min = 0.01,
                  max = 1,
                  value = alphL),
    sliderInput("alphM",
                  "\\(\\alpha_M\\)",
                  min = 0.01,
                  max = 1,
                  value = alphM),
    
    sliderInput("repli",
                  "Replications",
                  min = 1,
                  max = 1000,
                  value = 50)

  
)  


#library(rlang)
source("mulama_roulette_croupier.R")

gamble=function(input){
         # Collect the parameters


  
       firms=input$firms
       periods=input$periods
       alplhL=input$alphL
       alplhM=input$alphM
       repli=input$repli
  
       keys   <- c("firms", 
                   "periods", 
                   "alphL", 
                   "alphM", 
                   "gam", 
                   "signua", 
                   "signulam",
                   "signumu",
                   "sigalphmu",
                   "signuk",
                   "signul",
                   "philam",
                   "phia","repli")
       values=c()
       
       for(kk in keys){
         expr=paste0("values=c(values,",kk,")")
         eval(parse(text=expr))
         #print(expr)
        }
       
       params <- setNames(as.list(values), keys)
       
       res=monte(params)
       return(res)
       #output$summary=renderText(res)
  #output$distPlot <- renderPlot({
  #  hist(rnorm(input$obs))
  }
#textf()

#values <- reactiveValues(A=textf)

renderText({
  rr_df=gamble(input)
  
  library(ggplot2)
  output$gam=renderPlot(rr_df %>% ggplot(aes(x=gam))+geom_density()+
    geom_vline(xintercept = gam,         color = "blue", size=1.5)+
      xlab(expression(gamma))+
    theme_minimal())

  output$alphM=renderPlot(rr_df %>% ggplot(aes(x=alphM))+geom_density()+
    geom_vline(xintercept = alphM,       color = "blue", size=1.5)+
    theme_minimal())
  
  output$alphL=renderPlot(rr_df %>% ggplot(aes(x=alphL))+geom_density()+
    geom_vline(xintercept = alphL,       color = "blue", size=1.5)+
    theme_minimal())
  
  summary(rr_df)

})

```

# Monte Carlo Results

## Returns to scale $\gamma$

```{r,echo=FALSE}
library(dplyr)
library(shinycssloaders)
plotOutput("gam")

```


## Elasticity of output w.r.t materials

```{r}
plotOutput("alphM")%>% withSpinner(color="#0dc5c1")

```


## Elasticity of output w.r.t labour

```{r}
plotOutput("alphL")%>% withSpinner(color="#0dc5c1")

```


```{r,echo=FALSE, message=FALSE}
#library(DT)
#DT::renderDataTable({vars })

```




